---
title: "Lab 6 Comparing means"
author: "Michael Slaughter"
date: "`r Sys.Date()`"
output: github_document
---

Fill out this report and submit it as your completed assignment.

You can view the R markdown script that created this report here: [README.Rmd](README.Rmd)

## $t$-test

Researchers studying the number of electric fish species living in various parts of the Amazon basin were interested in whether the presence of tributaries affected the local number of electric fish species in the main rivers (Fernandes et al. 2004).

They counted the number of electric fish species above and below the entrance point of a major tributary at 12 different river locations.

The data is provided in your GitHub repository.

For each question below, write a sentence answering the question and show the code you used to come up with the answer, if applicable.

### Question A

> Test the hypothesis that the tributaries have no effect on the number of species of electric fish.

```{r t-test}
library(tidyverse)

fish <- read_csv("chap12q19ElectricFish.csv")

fish_long <- 
  pivot_longer(fish, speciesUpstream:speciesDownstream,
               names_to = "location",
               values_to = "species") %>% 
  mutate(location = str_remove(location, c("species"))) %>% 
  print()

fishMean <-
  fish_long%>% 
  group_by(location) %>% 
  summarize(
    n = n(),
    mean = mean(species),
    sd = sd(species),
    sem = sd/sqrt(n),
    upper = mean + 1.96 * sem,
    lower = mean - 1.96 * sem
  ) %>% 
  print()


fish_ttest <- t.test(species ~ location, data = fish_long)
fish_ttest$estimate

fish_ttest

```

ANSWER

### Question B

> What is the difference in the mean numbers of species between areas upstream and downstream of a tributary? What is the 95% confidence interval of this difference in means?

The difference between the two mean numbers is about 2 and the 95% confidence interval is between -4.6 and 8.3.

### Question C

> State the assumptions that you had to make to complete parts (A) and (B). Create a graph to assess whether one of those assumptions was met.

We had to assume whether there is or there is not a difference in the number of species upstream vs downstream. Using the following histogram and the T-test performed earlier, we can conclude that there is not a significant difference between species upstream vs downstream.

```{r}
fish_long %>% 
  ggplot(aes(x = species)) +
  geom_histogram(
    aes(fill = location), 
    bins = 6, 
    alpha = 0.5, 
    position = "identity"
  ) +
  scale_fill_manual(values = c("darkorange","cyan4")) +
  theme_minimal()+
  facet_wrap(~ location, ncol=1
)

```

## ANOVA

Fiddler crabs are so called because males have a greatly enlarged "major" claw, which is used to attract females and to defend a burrow.

Darnell and Munguia (2011) recently suggested that this appendage might also act as a heat sink, keeping males cooler while out of the burrow on hot days.

To test this, they placed four groups of crabs into separate plastic cups and supplied a source of radiant heat (60-watt light bulb) from above. The four groups were intact male crabs, male crabs with the major claw removed; male crabs with the other (minor) claw removed (control); and intact female fiddler crabs.

They measured the body temperature of crabs every 10 minutes for 1.5 hours. These measurements were used to calculate a rate of heat gain for every individual crab in degrees C/log minute. Rates of heat gain for all crabs are provided in the accompanying data file.

### Question D

> Graph the distribution of body temperatures for each crab type:
```{r}
```

### Question E

> Does body temperature vary among crab types? State the null and alternative hypothesis, conduct and ANOVA, and interpret the results.
```{r}
```